Fermi and eROSITA bubbles

### 2021-12-17 paper.tex
update

  \begin{equation}
    \Phi_{\text{total}} = \Phi_{\text{disk}} + \Phi_{\text{halo}},
  \end{equation}

@@

  \begin{equation}
    \Phi_{\text{disk}}=\
    2\sigma^2_{\text{disk}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{disk}}^{\text{peak}}}{\sigma^2_{\text{disk}}}}\right),
  \end{equation}

  is the potential of a plane-parallel isothermal slab contributed by stars within the Galactic plane.

  The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
  for the atmosphere gas can be derived from the isothermal and hydrostatic equilibrium condition,\
  given by

  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{if z > $z_{0}$}\\
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{if z > $z_{0}$}
     \end{cases}
  \end{equation}

@@

>>>>

  \begin{equation}
    \Phi_{\text{total}} = \Phi_{\text{bulge}} + \Phi_{\text{halo}},
  \end{equation}

@@

  \begin{equation}
    \Phi_{\text{bulge}}=\
    2\sigma^2_{\text{bulge}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
  \end{equation}

  is the potential of a plane-parallel isothermal slab mainly contributed by stars within the Galactic plane.

  The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
  for the gas can be derived from the isothermal and hydrostatic equilibrium condition,\
  given by

  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{bulge}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{bulge}}/m}\right] & \text{, if $|z| < z_{0}$,}\\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{, otherwise.}
     \end{cases}
  \end{equation}

  where $\rho_{\text{bulge}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
  of the bulge and the atmosphere at the $z=0$ plane.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\begin{tabular}{@{}llc@{}}
\toprule
Parameter                           & Description                   & Value                         \\ \midrule
Potential \& halo                   &                               &                               \\
$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge  & 100 km/s                      \\
$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$ \\
$v_{\text{halo}}$                   &                               & 131.5 km/s                    \\
$d_{\text{h}}$                      &                               & 12 kpc                        \\
Atmosphere                          &                               &                               \\
$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                    \\
Disk                                &                               &                               \\
$z_{0}$                             & Scale height of disk          & 100 pc                        \\
$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$          \\
$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                    \\ \bottomrule
\end{tabular}
\end{table*}
